Omics-based Single Step Trait Prediction

### 2017-03-30 paper/manuscript.tex
Rearrange inbred combi plot and PCA plot

Regarding the hybrid material, a PCA carried out separately for the two groups
of parental inbred lines showed that the entire genetic space in each group 
was covered well by genotypes that had both, transcriptomic and genomic data 
(Fig. \ref{fig:UHOH-PCA}).

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/uhoh_dent_flint_pca.pdf}
\caption{
  Principal component (PC) analysis of the two heterotic groups of the maize 
  hybrids.
  All inbred lines, which are covered by genomic and transcriptomic features
  are depicted as orange triangles whereas genotypes for which only genomic
  information are available are depicted as blue dots.
}
\label{fig:UHOH-PCA}
\end{figure}

>>>>

Regarding the hybrid material, a PCA carried out separately for the two groups
of parental inbred lines showed that the entire genetic space in each group 
was covered well by genotypes that had both, transcriptomic and genomic data 
(Fig. \ref{fig:PCA}).

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/diversity_dent_flint_pca.pdf}
\caption{
  Principal component (PC) analysis i) of the 211 tropical/subtropical lines 
  from the maize diversity panel, ii) of the 142 Dent parent lines of the 1,521
  maize hybrids and iii) of the 103 Flint parent lines of the maize hybrids.
  All inbred lines, which are covered by genomic and transcriptomic features
  are depicted as orange triangles whereas genotypes for which only genomic
  information are available are depicted as blue dots.
}
\label{fig:PCA}
\end{figure}
